Foregrounds in Wide--Field Redshifted 21~cm Power Spectra

### 2015-02-10 ms.tex
Add summary paragraph to Delay Spectrum section
from fb0bec1:
============

In ms.tex,

(*) Add summary paragraph to Delay Spectrum section
(*) Change wording in Wide-field measurements section slightly
(*) Remove citation of Tingay et al.(2013) in subsection Instrument
Model
(*) Rename subsection Fourier Delay Space to Delay Space
(*) Change caption to figure on wide-field effects slightly

Note that visibilities from different baselines have not been averaged together in this analysis.

\subsection{Fourier Delay Space}\label{sec:delay-space}

@@

Figure~\ref{fig:usm} shows the wide--field delay power spectrum response of a uniformly illuminated sky with no spectral variation measured by antenna elements arranged identical to that in the MWA antenna array layout \citep{bea12} with a uniform power pattern across the sky and a bandwidth of 30.72~MHz centered around 185~MHz (refer to \S\ref{sec:instrument_model} for a detailed description of the instrument model). Notice the features arising due to the direction--dependent solid angle term and the steep rise in power towards the horizon limits. Wide--field effects are prevalent on all antenna spacings, including the longest ones used in this study.

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figure3.eps}
\includegraphics[width=\linewidth]{figure2.eps}
\caption{Wide--field effects on delay power spectra produced with a uniform sky brightness distribution measured by antenna pairs with a uniform power pattern across the visible hemisphere. The non--zero response of the interferometer array to a uniform brightness distribution and the prominent {\it edge brightening} close to the horizon delay limits are wide--field effects. These are prevalent on all antenna spacings and are generic to all instruments used in wide--field measurements. \label{fig:usm}}
\end{figure}

@@

{\bf In our present study, we use a latitude of -26.701\arcdeg~ and an antenna layout identical to that of the MWA \citep{bea12} for the observatory. The array is arranged as a centrally condensed core of $\sim$~300~m --- there are many spacings in the range 5--50~m --- and a radial density that falls off as the inverse of the radius, with the longest baselines at 3~km. Here we focus on antenna spacings $|\boldsymbol{b}| \le 200$~m (spatial scales relevant to reionization). Their deviation from coplanarity is negligible. For geometrical intuition, we restrict the orientation ($\theta_b$, measured anti-clockwise from East) of all baselines to lie in the range $-67.5\arcdeg \leq \theta_b < 112.5\arcdeg$. Baselines oriented in the other half--plane measure conjugate visibilities with delays of equal magnitude but of opposite sign and hence are ignored in our analysis. We choose an observing frequency of 185~MHz ($z\simeq 6.68$) and a flat passband of width $\Delta B = 30.72$~MHz to roughly match those of ongoing MWA EoR observations. See \citet{tin13} for a detailed description of the MWA instrument}.

>>>>

In summary, the delay spectrum, $V_{b\tau}$, is obtained from {\it visibilities} which are the basic data blocks measured by each antenna pair, using equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform}. $V_{b\tau}$ captures all the effects of EoR H{\sc i} signal corruption caused by foregrounds and the instrument. At the same time, it is closely related to the sought power spectrum containing critical information about spatial scales. In using the delay spectrum technique, visibilities from different baselines have not been averaged together.

\subsection{Delay Space}\label{sec:delay-space}

@@

Figure~\ref{fig:usm} shows the wide--field delay power spectrum of a uniformly illuminated sky with no spectral variation measured by antenna elements arranged identical to that in the MWA antenna array layout \citep{bea12} with a uniform power pattern across the sky and a bandwidth of 30.72~MHz centered around 185~MHz (refer to \S\ref{sec:instrument_model} for a detailed description of the instrument model). Notice the steep rise in power towards the horizon limits. These wide--field effects are prevalent on all antenna spacings, including the longest ones used in this study.

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figure3.eps}
\includegraphics[width=\linewidth]{figure2.eps}
\caption{Wide--field effects on delay power spectra produced with a uniform sky brightness distribution measured by antenna pairs with a uniform power pattern across the visible hemisphere. Delay power spectra are obtained using equations~\ref{eqn:obsvis}, \ref{eqn:delay-transform} and \ref{eqn:delay-power-spectrum} for each baseline, which are then stacked by baseline length. The axes correspond to cosmological dimensions. The non--zero response of the interferometer array to a uniform brightness distribution and the prominent {\it edge brightening} close to the horizon delay limits are wide--field effects. These are prevalent on all antenna spacings and are generic to all instruments used in wide--field measurements. \label{fig:usm}}
\end{figure}

@@

{\bf In our present study, we use a latitude of -26.701\arcdeg~ and an antenna layout identical to that of the MWA \citep{bea12} for the observatory. The array is arranged as a centrally condensed core of $\sim$~300~m --- there are many spacings in the range 5--50~m --- and a radial density that falls off as the inverse of the radius, with the longest baselines at 3~km. Here we focus on antenna spacings $|\boldsymbol{b}| \le 200$~m (spatial scales relevant to reionization). Their deviation from coplanarity is negligible. For geometrical intuition, we restrict the orientation ($\theta_b$, measured anti-clockwise from East) of all baselines to lie in the range $-67.5\arcdeg \leq \theta_b < 112.5\arcdeg$. Baselines oriented in the other half--plane measure conjugate visibilities with delays of equal magnitude but of opposite sign and hence are ignored in our analysis. We choose an observing frequency of 185~MHz ($z\simeq 6.68$) and a flat passband of width $\Delta B = 30.72$~MHz to roughly match those of ongoing MWA EoR observations}.
